The error when inferring phylogenies with incipient species by a Birth-Death model

### 2018-04-11 article.tex
Visualize difference in sampling

The model prior most relevant here, is the tree prior. The tree prior
embodies the assumed speciation model. Each speciation model has a
different expected branch length distribution. It has been shown 
[NOTE: where?] that the effect of the prior on the posterior distribution 
of trees can be substantial.

@@

From an alignment, we run a Bayesian analysis and create a posterior, 
using the phylogetic tool BEAST2. We assume a
JC69 nucleotide substitution (as we do use that), a strict clock model (as
we have that) and a Birth-Death tree prior (as this simplification is the goal
of this research). Additionally, we assume a MRCA prior with a normal distribution
with a mean of the crown age, and a standard deviation of 0.001 time units. 0.001
time units equates to 1000 years, which is the same resolution as which the
alignment is created. After discarding a burn-in of 10\%, the MCMC algorithm must 
result in an ESS of the posterior of at least 200 and the MCMC sampling interval is 
chosen as such that this is the case for all simulations. For simulations
with an ESS below 200, their MCMC sampling interval is doubled up until
the ESS exceeds 200.

>>>>

The model prior most relevant here, is the tree prior. The tree prior
embodies the assumed speciation model. Each speciation model has a
different expected branch length distribution. It has been shown 
[Moeller, du Plessis, Stadler. 2018] that the effect of the prior on the posterior distribution 
of trees can be substantial.

@@

From an alignment, we run a Bayesian analysis and create a posterior, 
using the phylogetic tool BEAST2. We assume a
JC69 nucleotide substitution (as we do use that), a strict clock model with 
the same fixed rate as used in the simulation of the alignment (as
we have that) and a Birth-Death tree prior (as this simplification is the goal
of this research). Additionally, we assume a MRCA prior with a normal distribution
with a mean of the crown age, and a standard deviation of 0.001 time units. 0.001
time units equates to 1000 years, which is the same resolution as which the
alignment is created. After discarding a burn-in of 10\%, the MCMC algorithm must 
result in an ESS of the posterior of at least 200 and the MCMC sampling interval is 
chosen as such that this is the case for all simulations. For simulations
with an ESS below 200, their MCMC sampling interval is doubled up until
the ESS exceeds 200.
